### 2014-06-06 introduction.tex
8 pages

Multi-layered convolutional models (CNNs) have recently been shown to offer impressive levels of performance on visual detection tasks, by applying deep CNNs trained on object recognition tasks to multiple candidate image windows in a scene \cite{Sermanet-ICLR-2014,Girshick-CVPR-2014}.
While convolutional models are inherently efficient to implement, as convolution itself is a parallelizable and long studied computational primitive, the amount of work to perform complete inference at all candidate region windows is considerable.

@@

In this paper, we investigate a novel approach for speeding up R-CNN by proposing a general technique for accelerating CNNs applied to class imbalanced data (such as in object detection).
We bring the classical idea of a cascade to CNNs by inserting a \emph{reject} option between layers of the CNN.
When the CNN processes batches of images, which is standard for many applications, the reject layers allows the CNN to ``thin'' the batch as it progresses through the network, thus saving processing time.

>>>>

Multi-layered convolutional models (CNNs) have recently demonstrated impressive levels of performance on visual detection tasks, by applying deep CNNs trained on object recognition tasks to multiple candidate image windows in a scene \cite{Sermanet-ICLR-2014,Girshick-CVPR-2014}.
While convolutional models are inherently efficient to implement, as convolution itself is a parallelizable and long studied computational primitive, the amount of work to perform complete inference at all candidate region windows is considerable.

@@

In this paper, we investigate a novel approach for speeding up R-CNN by proposing a general technique for accelerating CNNs applied to class imbalanced data (such as in object detection).
We bring the classic idea of the cascade to CNNs by inserting a \emph{reject} option between CNN layers.
When the CNN processes batches of images, which is standard for many applications, the reject layers allows the CNN to ``thin'' the batch as it progresses through the network, thus saving processing time.
